Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Section explanation modification

    Section 2, contains a quick overview of some aspects used by different authors
    in order to tackle this problem, their design and basic functionality, in
    Section 3 the description of the current state of the project is explained, from
    %% The following sentence is not clear.
    the basis of the development, modification to the original proposed method as 
    well as different approaches that were taken to solve the problem.
    % to the different methods that have been used to
    %progress on the different sections of the project, 
    % Normaly there is no "Future Work" section is put together with Conclusions - MG
    finally in Section 4 we provide our conclusions about the development of this
    paper as well as improvements that can help to refine the proposed work.

>>>>

    Section 2, contains a quick overview of some aspects used by different authors
    in order to tackle this problem, their design and basic functionality, in
    Section 3 the description of the current state of the project is explained, from
    %% The following sentence is not clear.
    the way the candidate solutions are represented, to the way the mutations are applied 
    to them, as well as the way we use our fitness fucntion to determine the playability
    and complexity of the generated levels, 
    %the basis of the development, modification to the original proposed method as 
    %well as different approaches that were taken to solve the problem.
    % to the different methods that have been used to
    %progress on the different sections of the project, 
    % Normaly there is no "Future Work" section is put together with Conclusions - MG
    finally in Section 4 we provide our conclusions about the development of this
    paper as well as improvements that can help to refine the proposed work.

    %Maybe like this? JSH
